Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Downscaling in the Swiss Alps

### 2016-02-07 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Renaming figures.

\usepackage{multirow}
\usepackage{gensymb}
\usepackage{subcaption}

@@

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_map.pdf}}
	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
	\label{fig:map}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/figure_spatial_win_z4.pdf}}
	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo.pdf}}
	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo.pdf}}
	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_calib.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
	\label{fig:crossing_4Zo_calib}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_valid.pdf}}
	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
	\label{fig:crossing_4Zo_valid}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_spatial_win_z4-hi2.pdf}}
	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo-2MIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-2HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-4HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo-2HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues.pdf}}
	\caption{Number of analogues for the different regions and the various methods resulting from the optimization. Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
	\label{fig:figure_nb_analogues}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues_relationships.pdf}}
	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
	\label{fig:figure_nb_analogues_relationships}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_calib.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
	\label{fig:crossing_4Zo-2MIo_calib}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_valid.pdf}}
	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
	\label{fig:crossing_4Zo-2MIo_valid}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights.pdf}}
	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
	\label{fig:levels_weights}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights_average.pdf}}
	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
	\label{fig:levels_weights_average}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=7.5cm]{figures/figure_evolution.pdf}}
	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}

>>>>

\usepackage{multirow}
\usepackage{gensymb}

@@

\begin{figure}[t]
	\centerline{\includegraphics[width=8.8cm]{figures/fig01.pdf}}
	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
	\label{fig:map}
\end{figure}

\begin{figure}[t]
	\centerline{\includegraphics[width=8.4cm]{figures/fig02.pdf}}
	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig03.pdf}}
	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
	\label{fig:crossing_4Zo_calib}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
	\label{fig:crossing_4Zo_valid}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/fig07.pdf}}
	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels). The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_4Zo-2MIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-2HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrpss_4Zo-4HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
	\label{fig:figure_dcrps_comp_4Zo-2HIo}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
	\caption{Number of analogues for the different regions and the various methods resulting from the optimization. Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
	\label{fig:figure_nb_analogues}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
	\label{fig:figure_nb_analogues_relationships}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
	\label{fig:crossing_4Zo-2MIo_calib}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.4cm]{figures/fig14.pdf}}
	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
	\label{fig:crossing_4Zo-2MIo_valid}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig15.pdf}}
	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
	\label{fig:levels_weights}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
	\label{fig:levels_weights_average}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=7.5cm]{figures/fig17.pdf}}
	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
	\label{fig:evolution}
\end{figure}
